Understanding meta-analysis through data simulation with application to power analysis

### 2023-09-11 documents/paper/supplementary.Rmd
better folder structure

The previous code simulated a *compound symmetry* (CS) structure where all variances ($\tau^2$) and covariances ($\rho$) are the same. There could be different structures of the $T$ matrix that are clearly explained in the `metafor::rma.mv()` documentation (see https://wviechtb.github.io/metafor/reference/rma.mv.html#specifying-random-effects). For the sake of simplicity we will use the CS structure. We can use the `sim_T()` function that given the number of studies $k$, outcomes $p$, the vector of $\tau^2$ and the correlation $\rho$ generates the random-effect adjustments^[The function allow to specify heterogeneous $\tau^2$ values where the CS structure assume the same $\tau^2$ for each outcome. Using a fixed $\rho$ and different $\tau^2$ will create what `rma.mv()` calls a *heteroscedastic compound symmetric structure* thus a matrix where the correlation is the same between outcomes and each outcome has a different $\tau^2$ value].

>>>>

The previous code simulated a *compound symmetry* (CS) structure where all variances ($\tau^2$) and covariances ($\rho$) are the same. There could be different structures of the $T$ matrix that are clearly explained in the `metafor::rma.mv()` documentation (see https://wviechtb.github.io/metafor/reference/rma.mv.html#specifying-random-effects). For the sake of simplicity we will use the CS structure. We can use the `sim_T()` function that given the number of studies $k$, outcomes $p$, the vector of $\tau^2$ and the correlation $\rho$ generates the random-effect adjustments^[The function allow to specify heterogeneous $\tau^2$ values where the CS structure assume the same $\tau^2$ for each outcome. Using a fixed $\rho$ and different $\tau^2$ will create what `rma.mv()` calls a *heteroscedastic compound symmetry structure* thus a matrix where the correlation is the same between outcomes and each outcome has a different $\tau^2$ value].
